Simulating dynein's powerstroke using Brownian dynamics

### 2017-05-12 thesis/latex/thesis.tex
Thesis: Begin work on theory section.

\section{Cianfrocco model for dynein stepping}
Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts. Somehow the protein interacts with nucleotides and microtubules in a way that allows it to reliably move through the cell. The Cianfrocco model presented below takes these facts and string them together into cohesive cycles which might explain how dynein walks.\\

@@

%% \textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}. The specialness of ATP is that it can be broken down into ADP, which causes another conformation change back to state I. Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\

@@

\section{Model features}
The purpose of this project is to find if a minimal set of features is capable of reproducing dynein's stepping behavior. To test this hypothesis, these features are put into a model and simulated. A schematic of the model is pictured in Figure \ref{fig:model-intro} and described below.\\

\textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle. It would basically show all events occuring at two times: unbinding or rebinding.}\\

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
  \caption{Dynein model schematics.}{Representations of onebound (left) and bothbound (right) dynein models.}
  \label{ob_fig}
\end{figure}

@@

>>>>

\section{Cianfrocco model for dynein stepping}
\label{sec:cianfrocco-model}
Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts. Somehow the protein interacts with nucleotides and microtubules in a way that allows it to reliably move through the cell. The Cianfrocco model presented below takes these facts and string them together into cohesive cycles which might explain how dynein walks.\\

@@

@@

\section{Building the model}
The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model \ref{sec:cianfrocco-model} would behave in a cell. In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation. Creating such a model is a balance between accuracy and computational efficiency. The model must be complex enough to correspond well to dynein, but not be so complex that it cannot be simulated in a reasonable amount of time. Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be infeasibly computationally expensive to simulate a dynein step. Thus, many approximations are made about dynein to simplify the simulation.\\

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/theory-onebound}
  \includegraphics[width=.45\textwidth]{../../figures/theory-bothbound}
  \caption{Spatial representation of the dynein dynamic model.}{Dynein is simplified to a two-dimensional point-particle system. Five points in total represent the two MTBDs, two motor domains and one tail domain. These points are connected by rigid rods. Although approximated as points, each domain has a radius $R$ associated with it used for drag calculations.}
  \label{fig:theory-intro}
\end{figure}

%% \textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle. It would basically show all events occuring at two times: unbinding or rebinding.}\\

@@

@@

%thoughts
%% \textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}. The specialness of ATP is that it can be broken down into ADP, which causes another conformation change back to state I. Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\
